Modeling potential JCPOA diversion scenarios using Cyclus

### 2018-01-27 paper.tex
simplify caption

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.68]{flow_case_2_no_recy.pdf}
  \caption{Illustration of the material flow between the different level of
      cascades without tail recycling, in this diagram, nu\_src corresponds to an
  infinite source of natural uranium, cascade\_ $\{n\}$ and storage\_ $\{n\}$
      corresponds to the cascade and the storage getting the
      products of the cascades at the level $\{n\}$.}\label{fig:flow}
\end{figure}

>>>>

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.68]{flow_case_2_no_recy.pdf}
  \caption{Illustration of the material flow between the different level of
      cascades without tail recycling, in this diagram, nu\_src corresponds to
      an infinite source of natural uranium, cascade\_ $\{n\}$ and storage\_
      $\{n\}$ to the cascade and the storage getting the products of the
      cascades at the level $\{n\}$.}\label{fig:flow}
\end{figure}
